---
title: "QMM GP"
author: "HARI VINAYAK"
date: "2023-11-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##summary

1. **Production Optimization:**
   - We aimed to maximize production using variables (X1, X2, X3), but the result shows "0" for X1 and X2. This means we can't make 20 units of Product 1 and 15 units of Product 2. Now, our focus is on producing only 15 units of Product 3, which brings in the most revenue.

2. **Workforce Management:**
   - Despite targeting a workforce of 50 hundred employees, we exceeded it by 25 hundred employees (ytp), leading to penalties for surpassing employment limits.

3. **Financial Outlook:**
   - Looking ahead, both y2p and y2m are "0," indicating a stable financial forecast for the next year. There's no expected increase or decrease compared to the current fiscal year.

4. **Objective Function Result:**
   - The bottom line: $225 million. This number summarizes the financial impact of our production and workforce decisions.


```{r}
library(lpSolveAPI)
```


```{r}
x <- read.lp("GP.lp")
x                         
```

## Solve
```{r}
solve(x)
get.objective(x)
get.variables(x)
get.constraints(x)
```

```{r}
get.sensitivity.rhs(x)
get.sensitivity.objex(x)
```